Beyond Adaptive Web Design

### 2014-02-20 paper/paper.tex
refactor: verify the usefulness of the proposed concept

\documentclass{iitsrc}
\usepackage{graphicx}
\usepackage{mflogo}
\usepackage[utf8]{inputenc}%some compilers use utf8x and need the prerendredUnicode characters
%\PrerenderUnicode{áäčďéíľĺňóôŕšťúýžÁÄČĎÉÍĽĹŇÓÔŔŠŤÚÝŽ}

% Please do not remove the following commands:
\editpages{1}{8}
\hyphenation{pha-blets}

@@

There have been made series of experiments on both adaptive input methods and web components. To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects. All of them have been released as open source and are available on GitHub.

We have tracked amount of saved web traffic, interest in alternative input methods and received a lot of feedback from the community.

@@

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.7\textwidth]{../images/videomotion}
        \caption{Converting video stream into motion vector}
        \label{fig:videomotion}
    \end{center}
\end{figure}

@@

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.7\textwidth]{../images/maps.png}
        \caption{Maps component}
        \label{fig:maps}
    \end{center}
\end{figure}

>>>>

\documentclass{iitsrc}
\usepackage{graphicx}
\usepackage{mflogo}
\usepackage{url}
\usepackage[utf8]{inputenc}%some compilers use utf8x and need the prerendredUnicode characters
%\PrerenderUnicode{áäčďéíľĺňóôŕšťúýžÁÄČĎÉÍĽĹŇÓÔŔŠŤÚÝŽ}

% Please do not remove the following commands:
\editpages{1}{6}
\hyphenation{pha-blets}

@@

We have detected several web componenets and input methods and tried to verify which of them is more useful for the web developers. There have been made series of experiments on both adaptive input methods and web components. To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects. All of them have been released as open source and are available on GitHub~\footnotemark.

\footnotetext{The modules and components we used to verify the usefulness of the proposed concept are available on GitHub \url{https://github.com/angular-adaptive}}

We have tracked amount of saved web traffic and web requests, webpage rendering time and interest in alternative input methods. We have also received a lot of feedback from the community which helped us to verify the proposed concept.

@@

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.8\textwidth]{../images/videomotion}
        \caption{Converting video stream into motion vector}
        \label{fig:videomotion}
    \end{center}
\end{figure}

@@

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.8\textwidth]{../images/maps.png}
        \caption{Maps component}
        \label{fig:maps}
    \end{center}
\end{figure}
